On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients

### 2018-07-12 docs/mvfits_paper/mvf.tex
adding Ed to doc

@@

\author{L. London}
\affiliation{School of Physics and Astronomy, Cardiff University, The Parade, Cardiff, CF24 3AA, United Kingdom}

@@

Let's start by applying \gmvr{} to a fiducial scalar function,

@@

  f(x_0,x_1) = 50 + \frac{1.1 +0.2 x_0+0.5 x_1+x_0 x_1}{ 0.9 + x_0^2 + x_1^2 }

@@

@@

@@

%
\begin{figure}[htb]
  %
  \includegraphics[width=0.45\textwidth]{fig/issue3_pgreedy.pdf}
  %
	\caption{ Convergence of greedy process for \gmvr{} toy problem. }
  %
\end{figure}

>>>>

\newcommand{\Cardiff}{School of Physics and Astronomy, Cardiff University, Queens Buildings, Cardiff, CF24 3AA, United Kingdom}

@@

\author{L. London}
\affiliation{\Cardiff}
\author{Edward Fauchon-Jones}
\affiliation{\Cardiff}

@@

Here, our goal is to very brielfy assess
Let's start by applying \gmvr{} to a fiducial scalar function of the form

@@

  % f(x_0,x_1) = 50 + \frac{1.1 +0.2 x_0+0.5 x_1+x_0 x_1}{ 0.9 + x_0^2 + x_1^2 }
  f(x_0,x_1) = \mu + \sigma \, \left( \, \frac{a_0 +a_1  x_0 + a_2 x_1 + a_3 x_0 x_1}{ 1 + b_1 \, x_0^2 +  b_2 x_1^2 } \, \right) + 0.05 \, n \; ,

@@

where $n$ is a uniform random variable on $[-1,1]$.
Towards easily identifying test values for $a_j$ and $b_k$ with those recovered, it is more straightforward to distribute $\sigma$ to the denominator, yielding
  \label{eq:gmvrtoy1}
  f(x_0,x_1) = \mu + \, \frac{a_0 +a_1  x_0 + a_2 x_1 + a_3 x_0 x_1}{ 1/\sigma + (b_1/\sigma) \, x_0^2 +  (b_2/\sigma) x_1^2 } + 0.05 \, n \; .
Under this perspective we will consider test data generated with the following parameters:
$\mu = 50.0$,
$a_0 = 1.1$,
$a_1 = 0.2$,
$a_3 = 1.0$,
$1/\sigma = 0.9$,
$b_1/\sigma = b_2/\sigma = 1.0$.
\par To generate the test data, \eqn{eq:gmvrtoy1} is evaluated with 25 points in $x_0$ and $x_1$, where each is between -3 and 3.
\par \fig{fig:gmvrtoy} shows the application of \gmvr{} to this fiducial dataset.
\fig{fig:gmvrtoy}'s central bottom panel displays the distribution of fractional residuals, and demonstrates their approximately flat distribution. A gaussian fit to the fractional residuals is displayed only for optical comparison.
We find that the direct sample residuals are $99.46\%$ correlated with the input noise.
\par \fig{fig:gmvrtoy}'s left top and bottom panels show the convergence of Alg. (\ref{alg:A_gmvr})'s iterative refinement stage (i.e. its while-loop).
Here it is demonstrated that \gmvr{} converges exponentially, as expected given th.

@@

  \label{fig:gmvrtoy}

@@

%
\begin{figure}[htb]
  %
  \includegraphics[width=0.45\textwidth]{fig/issue3_pgreedy.pdf}
	\caption{ Convergence of greedy process for \gmvr{} toy problem. }
  %
\end{figure}
